A Case Study in Preserving a High Energy Physics Application

### 2014-01-17 paper.tex
Expand a bit on the analysis purpose.

Within the ongoing investigation of the Higgs boson at the CMS
detector, part of the LHC at CERN, the Higgs production in association
with two top quarks allows to measure the Higgs coupling strength to
top quarks.  As the Higgs boson cannot be detected itself, it has to
be reconstructed from its decay products.  The analysis discussed in
this section focuses on the Higgs decaying to two tau leptons, which
are reconstructed from particle showers.

>>>>

Within the ongoing investigation of the Higgs boson at the CMS
detector, part of the LHC at CERN, the Higgs production in association
with two top quarks allows to measure the Higgs coupling strength to
top quarks.  As the Higgs boson is to short-lived to be detected
itself, it has to be reconstructed from its decay products.  The
analysis discussed in this section focuses on the Higgs decaying to
two tau leptons, which are themselves reconstructed from particle
showers.  Within the analysis, events are identified that show a
signature of decay products compatible with both hadronic tau and top
decays.  Properties of such events are used to distinguish signal-like
(matching simulated Higgs decays) and background-like events and are
also used in further statistical analysis.
